---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# paperpile

<!-- badges: start -->
[![stability-experimental](https://img.shields.io/badge/stability-experimental-orange.svg)]()
<!-- badges: end -->

The goal of paperpile is to interact with paperpile from `R`.

## Installation

You can install the package by cloning and installing locally


## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(paperpile)
```

## Querying

### Default

```{r}
query('Holford and Sheiner 1981')
```

### Exact matches

```{r}
query('Holford and Sheiner 1981 - Pharmacokinetic and pharmacodynamic modeling in vivo.pdf',
      operator = '=')
```

```{r}
query('Holford and Sheiner 1981',operator = '=')
```

## Download file to local machine

```{r}
query('Holford and Sheiner 1981')%>%fetch()
```

## Interacting with exported bib file from paperpile
### Read in bib file as list

```{r}
bib <- paperpile::parse_bib()
```

### Convert the list to a tibble

```{r}
bib_tbl <- bib%>%
  bibble()

bib_tbl
```

### Filter the tibble using tidyverse packages

```{r}
keys <- bib_tbl%>%
  dplyr::filter(grepl('Knebel W',author,ignore.case = TRUE))%>%
  dplyr::pull(rowid)

keys

```

### Write subset of original bib file as new smaller bib file

```{r,eval=FALSE}
bib%>%write_bib(keys)
```

<details><summary>bib output</summary>

```{r,echo=FALSE}
bib%>%write_bib(keys)
```

</details>
